Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2023-07-19 ba_resubmit/kundinger_resubmit2.tex
more edits.

\textcolor{red}{Note that 	$\gamma_{Z_j, j}$ doesn't appear to be defined.}

@@

\textcolor{teal}{Observe that we compute the vectorized summations in (\ref{efficient_alpha}) and (\ref{efficient_beta}) more efficiently than the previous updates in (\ref{efficient_alpha}) and (\ref{efficient_beta}), which require summing over $n_A n_B$ record pairs for each field and agreement level.}

>>>>

\textcolor{teal}{In our derivations below, we assume the new update to the Gibbs sampler is $s+1$ and the current state of the sampler is $s.$ As to not overload notation, we suppress the state of the sampler until presenting the updates to each full conditional distribution based upon our computational proposals using hashing.}

\begin{enumerate}	
\item \textcolor{red}{Note that 	$\gamma_{Z_j, j}$ doesn't appear to be defined.}
\item \textcolor{red}{There appears to be no update for $\pi$ in this section.}
\item Make sure when you give the update for the new efficient full conditional, you give the s, s+1. Example, it's missing on the update for $m$ and $u$ so it's not immediately clear how one would draw this directly. Wouldn't it just be a vectorized Dirichlet, where the computational savings come from vectorizing the hyperparameters of the Dirichlet?
\end{enumerate}

@@

\textcolor{teal}{Observe that we compute the vectorized summations in (\ref{efficient_alpha}) and (\ref{efficient_beta}) more efficiently than the previous updates in (\ref{eqn:alpha_update}) and (\ref{eqn:beta_update}), which require summing over $n_A n_B$ record pairs for each field and agreement level.}

\textcolor{red}{Some statement regarding $\pi$ needs to go here even if it's that you draw from the same distribution as in the original sampler.}
